Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-09-23 main.Rmd
shorten abstract to 200 words

abstract: |
 Deconstructing a time index into time granularities can assist in exploration and automated analysis of large temporal data sets. This paper describes classes of time deconstructions using linear and cyclic time granularities. Linear time granularities respect the linear progression of time such as hours, days, weeks and months. Cyclic time granularities can be circular such as hour-of-the-day, quasi-circular such as day-of-the-month, and aperiodic such as public holidays. The hierarchical structure of granularities creates a nested ordering: hour-of-the-day and second-of-the-minute are single-order-up. Hour-of-the-week is multiple-order-up, because it passes over day-of-the-week. Methods are provided for creating all possible granularities for a time index. A recommendation algorithm provides an indication whether a pair of granularities can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").

@@

 The methods are implemented in the open source R package `gravitas`, providing functions for creating granularities and exploring the associated time series which are consistent with a tidy workflow (@Grolemund2018-po), and the probability distributions can be examined using the range of graphics available in `ggplot2` [@Wickham2009pk].
bibliography: [bibliography.bib]
preamble: >
  \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
  \def\mod{~\text{mod}~}
  \newtheorem{definition}{Definition}
  \usepackage{mathptmx}
  \usepackage{caption}
  \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
  \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
  \captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
  \def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
  \def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
output:
  bookdown::pdf_book:
    base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes
---

@@

This work provides tools for systematically exploring bivariate granularities within the tidy workflow. In particular, we

>>>>

abstract: |
 Deconstructing a time index into time granularities can assist in exploration and automated analysis of large temporal data sets. This paper describes classes of time deconstructions using linear and cyclic time granularities. Linear granularities respect the linear progression of time such as hours, days, weeks and months. Cyclic granularities can be circular such as hour-of-the-day, quasi-circular such as day-of-the-month, and aperiodic such as public holidays. The hierarchical structure of granularities creates a nested ordering: hour-of-the-day and second-of-the-minute are single-order-up. Hour-of-the-week is multiple-order-up, because it passes over day-of-the-week. Methods are provided for creating all possible granularities for a time index. A recommendation algorithm provides an indication whether a pair of granularities can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").

@@

 The methods implemented in the open source R package `gravitas` are consistent with a tidy workflow, with probability distributions examined using the range of graphics available in `ggplot2`.

bibliography: [bibliography.bib]
preamble: >
  \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
  \def\mod{~\text{mod}~}
  \newtheorem{definition}{Definition}
  \usepackage{mathptmx}
  \usepackage{caption}
  \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
  \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
  \captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
  \def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
  \def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
output:
  bookdown::pdf_book:
    base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes
---

@@

This work provides tools for systematically exploring bivariate granularities within the tidy workflow (@Grolemund2018-po). In particular, we
